Motmot: A Distributed Chat Protocol

### 2012-05-04 paper/paper.tex
Conclusion

Wheeee.

>>>>

\Motmot is a novel distributed chat protocol that offers features not present in
other chat protocols. Its reliance on the Paxos algorithm allow it to react
properly to the changing topology of chatting peers, and is the core improvement
on other protocols.

While we have not had a chance to test the protocol in practice, we believe that
\Motmot not only provides interesting technical guarantees, but is also usable
in practice.

In summary, we believe that \Motmot is the best thing since sliced bread.
